\Huge{Machine Learning} \\ \LARGE Nature's Quest: Deep Learning Exploration of Global Plant Traits from Images and Geodata

### 2024-03-29 paper/paper.tex
info sheet update

% discuss the results
The prediction of plant traits from images and geodata is a complex task that requires a CNN to learn and extract features from both images and geodata. The results of our work show that a CNN trained on just an image outperforms one trained on images and geodata. Though neither of the models elaborated here are necessarily good predictors, one of the main reasons for this is likely the complexity and nuance of the task. We now propose various directions for future work to improve the prediction capabilities of the models.

>>>>

% discuss the results
The prediction of plant traits from images and geodata is a complex task that requires a CNN to learn and extract features from both images and geodata. The results of our work show that a CNN trained on just an image outperforms one trained on images and geodata. Neither of the models elaborated here are necessarily good predictors, one of the main reasons for this is likely the complexity and nuance of the task regression task. We now propose various directions for future work to improve the prediction capabilities of the models.
